CLPFUDatabase: A suite of R packages for energy conversion chain analysis

### 2023-12-12 paper.Rmd
Paper now able to build again.
Added metapackage information

We created a suite of open-source `R` packages 
to assist SEA practitioners to analyze ECCs. 
The new packages enable analysis of any country in the world
across timespans of decades or longer.
In short, the new packages enable, for the first time, scalable SEA.
We used the new packages to create the CL-PFU database^["CL-PFU" 
is an initialism for "Country-Level
Primary, Final, and Useful."
The CL-PFU database contains many countries as well as 
continental and world aggregations.
Technically speaking, 
we create [matsindf][link-matsindf] data frames
stored as [pins][link-pins] on a pinboard, 
not SQL or similar databases.],
a new resource for the SEA community [@Marshall:2023aa].

@@

Further development followed selection of the PSUT framework.
First, the RUVY matrices carry the challenge that 
different countries and years 
have varying energy carriers (products) and
varying energy conversion machines (industries),
meaning that RUVY matrices 
have differing row names, differing column names, and differing sizes
from one country to another and for different years within the same country.
To circumvent this challenge, we created the
[matsbyname][link-matsbyname] package [@Heun-matsbyname:2023]
which enables matrix mathematics 
that respects row and column names, 
inserting **0** row or column vectors when needed.
Second,
we wanted to be able to perform _matrix_ mathematics 
as easily as _scalar_ mathematics
in `R` data frames
using [tidyverse][link-tidyverse] syntax [@Wickham:2019]. 
We developed the [matsindf][link-matsindf] package [@Heun-matsindf:2023]
to enable this functionality.
Finally, manipulating row and column names proved to be a challenge, 
especially for RUVY matrices in [matsindf][link-matsindf] data frames, so 
we developed the [RCLabels][link-rclabels] package [@Heun-RCLabels:2023]
to support the PSUT framework.
The table below summarizes these packages, 
all of which are generally useful and available on 
[CRAN][link-cran].

@@

The packages in the following table support creation of the CL-PFU database
are available on GitHub.

>>>>

We created a suite of open-source `R` packages 
and the metapackage `CLPFUDatabase`
to assist SEA practitioners to analyze ECCs. 
The new packages enable analysis of any country in the world
across timespans of decades or longer.
In short, the new packages enable, for the first time, scalable SEA.
We used the new packages to create the CL-PFU database^["CL-PFU" 
is an initialism for "Country-Level
Primary, Final, and Useful."
The CL-PFU database contains many countries as well as 
continental and world aggregations.
Technically speaking, 
we create [matsindf][link-matsindf] data frames
stored as [pins][link-pins] on a pinboard, 
not SQL or similar databases.],
a new resource for the SEA community [@Marshall:2023aa].

@@

Further development followed selection of the PSUT framework.
First, the RUVY matrices carry the challenge that 
different countries and years 
have varying energy carriers (products) and
varying energy conversion machines (industries),
meaning that RUVY matrices 
have differing row names, differing column names, and differing sizes
from one country to another and for different years within the same country.
To circumvent this challenge, we created the
[matsbyname][link-matsbyname] package [@Heun-matsbyname:2023]
which enables matrix mathematics 
that respects row and column names, 
inserting **0** row or column vectors when needed.
Second,
we wanted to be able to perform _matrix_ mathematics 
as easily as _scalar_ mathematics
in `R` data frames
using [tidyverse][link-tidyverse] syntax [@Wickham:2019]. 
We developed the [matsindf][link-matsindf] package [@Heun-matsindf:2023]
to enable this functionality.
Finally, manipulating row and column names proved to be a challenge, 
especially for RUVY matrices in [matsindf][link-matsindf] data frames, so 
we developed the [RCLabels][link-rclabels] package [@Heun-RCLabels:2023]
to assist.
The table below summarizes these packages, 
all of which are generally useful and available on 
[CRAN][link-cran].

@@

The packages in the following table are available on GitHub.
